OA Share

### 2020-12-09 analysis/006_license.Rmd
check for mirror journals

>>>>

### License for Mirror journals

```{sql, connection=con, output.var="els_yearly_mirror"}
SELECT  issued_year,
        container_title,
        COUNT(DISTINCT(doi)) as all_articles 
    FROM
        `api-project-764811344545.cr_dump_march_20.els_all_may_20`
    WHERE
        issued_year > 2014 
        and issued_year < 2020        
        and not    regexp_contains(title,'^Author Index$|^Back Cover|^Contents$|^Contents:|^Cover Image|^Cover Picture|^Editorial Board|^Front Cover|^Frontispiece|^Inside Back Cover|^Inside Cover|^Inside Front Cover|^Issue Information|^List of contents|^Masthead|^Title page|^Correction$|^Corrections to|^Corrections$|^Withdrawn')
        and (not regexp_contains(page, '^S') or page is NULL)
        and regexp_contains(container_title, '^[a-z|A-Z|0-9]+[^I]\\s? X{1}$')
    GROUP BY
        issued_year,
        container_title
```

```{r}
els_yearly_mirror
```

```{r}
sum(els_yearly_mirror$all_articles)
```
